MSTK: Mesh Toolkit, v 1.3 - DRAFT

### 2004-07-28 docs/MSTK.tex
*** empty log message ***

\item[]\textbf{\textit{void} MR\_Set\_Vertices(\textit{MRegion\_ptr}
    mregion, \textit{int} nv, \textit{MVertex\_ptr} *mvertices):} Set
  the vertices of the region. This routine will collect/build all
  lower order topological information (edges, edge directions in the
  face) as needed by the face. For standard elements, the vertices
  must be ordered as indicated in Appendix~\ref{app:reg_conventions},
  while \textbf{nf} can be 0 and \textbf{rfv\_template} can be NULL.
  For non-standard elements, \textbf{nf} is the number of faces of the
  polyhedron and \textbf{rfv\_template} gives the vertices used in each
  face. More precisely, \textbf{rfv\_template} has \textbf{nfv}
  pointers to integer array $i$. The first entry of each
  \textbf{rfv\_template$[i]$} represents the number of vertices in that
  face and the remaining entries represent the list of vertices of the
  face listed so that the face defined by them points outward.

>>>>

\item[]\textbf{\textit{void} MR\_Set\_Vertices(\textit{MRegion\_ptr}
    mregion, \textit{int} nv, \textit{MVertex\_ptr} *mvertices, 
    \textit{int} nf, \textit{int} **rfv\_template):} Set
  the vertices of the region. This routine will collect/build all
  lower order topological information (edges, edge directions in the
  face) as needed by the face. For standard elements, the vertices
  must be ordered as indicated in Appendix~\ref{app:reg_conventions},
  while \textbf{nf} can be 0 and \textbf{rfv\_template} can be NULL.
  For non-standard elements, \textbf{nf} is the number of faces of the
  polyhedron and \textbf{rfv\_template} gives the vertices used in each
  face. More precisely, \textbf{rfv\_template} has \textbf{nfv}
  pointers to integer array $i$. The first entry of each
  \textbf{rfv\_template$[i]$} represents the number of vertices in that
  face and the remaining entries represent the list of vertices of the
  face listed so that the face defined by them points out of the region.
